This is an example of article title

### 2025-04-10 paper/paper.tex
update future plans to match article updates

Future plans for the package and the method itself include an overhaul of the tolerance modeling scheme.
Currently, only dimensional tolerances are handled, but it should be discovered if more GD\&T tolerances can be incorporated into the model.
The current implementation supports only cylinders and planes, thus drilling and milling; it is a future research direction to extend the handled machining operations, e.g., to turning.

>>>>

Future plans for the package and the method itself include an overhaul of the tolerance modelling scheme.
It should be possible to generalize the current dimensional tolerances for  more GD\&T tolerances by introducing a new type hierarchy based on the current geometry type tree and a function interface for the optimization program.
Another direction of development is to extend the supported operations from drilling and milling to others, such as turning, although this is more a research question than an implementation.
